---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neoipcr - The R Package to Work With NeoIPC Data

<!-- badges: start -->

[![Codecov test coverage](https://codecov.io/gh/NeoIPC/neoipcr/graph/badge.svg)](https://app.codecov.io/gh/NeoIPC/neoipcr)

<!-- badges: end -->

The goal of neoipcr is to facilitate working with data from the NeoIPC project

## Installation

You can install the development version of neoipcr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("NeoIPC/neoipcr")
```

## Importing Data From DHIS2

To import data from a NeoIPC DHIS2 server use `import_dhis2()`. neoipcr is a
public library for *any* DHIS2 instance running the NeoIPC metadata package, so
it does not default to a specific host — pass your instance's `hostname`
to `dhis2_connection_options()` (with `scheme`/`port`/`path` if they differ
from the `https` / 443 / `/api` defaults). Credentials can be passed
directly (a personal access token, username/password, or session id), or left
to be resolved from environment variables (`NEOIPC_DHIS2_TOKEN`,
`NEOIPC_DHIS2_USER` + `NEOIPC_DHIS2_PASSWORD`, or `NEOIPC_DHIS2_SESSION_ID`),
falling back to an interactive prompt; see `?dhis2_connection_options`.

```{r example, eval=FALSE}
library(neoipcr)

connection <- dhis2_connection_options(hostname = "dhis2.example.org")
data <- import_dhis2(connection)
```

Alternatively, set the host in the `NEOIPC_DHIS2_HOST` environment variable
(alongside the credential variables above) and call `import_dhis2()` with no
arguments:

```{r example-env, eval=FALSE}
# NEOIPC_DHIS2_HOST and, e.g., NEOIPC_DHIS2_TOKEN set in the environment
data <- import_dhis2()
```

## Supported Versions

neoipcr is tested against the currently deployed DHIS2 version plus the tip of
each newer released line; `neoipcr_supported_versions()` returns the exact
list. Reading a server on an untested line is allowed but emits a warning. The
vocabulary neoipcr binds to — the `NEOIPC_CORE` program, the stage/option-set
codes, and the org-unit-group codes (`COUNTRY`, `HOSPITAL`, `NEO_DEPARTMENT`) —
is defined by the NeoIPC metadata package, not by any particular deployment.

```{r supported-versions, eval=FALSE}
neoipcr_supported_versions()
```
